---
title: "Getting started with binomial"
author: "Justin Le"
output: html_document
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
```

## Binomial
The package binomial returns the probability of getting a certain number of heads with a given number of trials. It also does some visualization with plots.

## Creating a bin variable
First create a bin variable that you can draw information from:

```{r}
bin_variable(trials = 5, prob = 0.5)
bin_variable
```
You can set the number of trials and the prob yourself. 
Running the bin_variable object gives information about the variable.

## Getting Probabilities
To get probability of getting a certain number of successes, use bin_choose to determine the combinations the tosses can take.

```{r}
bin_probability(success = 3, trials = 5, prob = 0.5)
```

## Getting plots
To create a histogram of a distribution, first create a distribtion object.
```{r}
bin_dist <- bin_distribution(trials = 5, prob = 0.5)
```
Then plot the object.

```{r}
plot(bin_dist)
```

You can do something similar to get cumulative graphs.

```{r}
bin_cumt <- bin_cumulative(trials = 5, prob = 0.5)
plot(bin_cumt)
```