---
title: "Workout 1"
author: "Justin Le"
output: github_document
---

```{r, message = F, warning = F, echo = FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(grid)
library(jpeg)
library(readr)
```

```{r, message = F, warning = F, echo = F, results ='hide'}
setwd("..")
shot_data <- read_csv("data/shots-data.csv")
```

```{r , message = F, warning = F, echo = F, results ='hide'}
#2pt effective shooting % by Player
curry_2pt_total <- nrow(shot_data[shot_data$name == "Steph Curry" & shot_data$shot_type == "2PT Field Goal",])
curry_2pt_made <- nrow(shot_data[shot_data$name == "Steph Curry" & shot_data$shot_type == "2PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
curry_2pt_percent <- curry_2pt_made/curry_2pt_total

draymond_2pt_total <- nrow(shot_data[shot_data$name == "Draymond Green" & shot_data$shot_type == "2PT Field Goal",])
draymond_2pt_made <- nrow(shot_data[shot_data$name == "Draymond Green" & shot_data$shot_type == "2PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
draymond_2pt_percent <- draymond_2pt_made/draymond_2pt_total

durant_2pt_total <- nrow(shot_data[shot_data$name == "Kevin Durant" & shot_data$shot_type == "2PT Field Goal",])
durant_2pt_made <- nrow(shot_data[shot_data$name == "Kevin Durant" & shot_data$shot_type == "2PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
durant_2pt_percent <- durant_2pt_made/durant_2pt_total

iguodala_2pt_total <- nrow(shot_data[shot_data$name == "Andre Iguodala" & shot_data$shot_type == "2PT Field Goal",])
iguodala_2pt_made <- nrow(shot_data[shot_data$name == "Andre Iguodala" & shot_data$shot_type == "2PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
iguodala_2pt_percent <- iguodala_2pt_made/iguodala_2pt_total

klay_2pt_total <- nrow(shot_data[shot_data$name == "Klay Thompson" & shot_data$shot_type == "2PT Field Goal",])
klay_2pt_made <- nrow(shot_data[shot_data$name == "Klay Thompson" & shot_data$shot_type == "2PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
klay_2pt_percent <- klay_2pt_made/klay_2pt_total

table_2pt <- data.frame("Name" = c("Steph Curry", "Draymond Green","Kevin Durant", "Andre Iguodala", "Klay Thompson"), "Total" = c(curry_2pt_total, draymond_2pt_total, durant_2pt_total, iguodala_2pt_total, klay_2pt_total), "Made" = c(curry_2pt_made, draymond_2pt_made, durant_2pt_made, iguodala_2pt_made, klay_2pt_made), "Perc_Made" = c(curry_2pt_percent, draymond_2pt_percent, durant_2pt_percent, iguodala_2pt_percent, klay_2pt_percent))
table_2pt$Perc_Made <- table_2pt$Perc_Made*100
table_2pt <- arrange(table_2pt, desc(table_2pt$Perc_Made))

```

```{r, message = F, warning = F, echo = F, results ='hide'}
#3pt effective shooting % by Player
curry_3pt_total <- nrow(shot_data[shot_data$name == "Steph Curry" & shot_data$shot_type == "3PT Field Goal",])
curry_3pt_made <- nrow(shot_data[shot_data$name == "Steph Curry" & shot_data$shot_type == "3PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
curry_3pt_percent <- curry_3pt_made/curry_3pt_total

draymond_3pt_total <- nrow(shot_data[shot_data$name == "Draymond Green" & shot_data$shot_type == "3PT Field Goal",])
draymond_3pt_made <- nrow(shot_data[shot_data$name == "Draymond Green" & shot_data$shot_type == "3PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
draymond_3pt_percent <- draymond_3pt_made/draymond_3pt_total

durant_3pt_total <- nrow(shot_data[shot_data$name == "Kevin Durant" & shot_data$shot_type == "3PT Field Goal",])
durant_3pt_made <- nrow(shot_data[shot_data$name == "Kevin Durant" & shot_data$shot_type == "3PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
durant_3pt_percent <- durant_3pt_made/durant_3pt_total

iguodala_3pt_total <- nrow(shot_data[shot_data$name == "Andre Iguodala" & shot_data$shot_type == "3PT Field Goal",])
iguodala_3pt_made <- nrow(shot_data[shot_data$name == "Andre Iguodala" & shot_data$shot_type == "3PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
iguodala_3pt_percent <- iguodala_3pt_made/iguodala_3pt_total

klay_3pt_total <- nrow(shot_data[shot_data$name == "Klay Thompson" & shot_data$shot_type == "3PT Field Goal",])
klay_3pt_made <- nrow(shot_data[shot_data$name == "Klay Thompson" & shot_data$shot_type == "3PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
klay_3pt_percent <- klay_3pt_made/klay_3pt_total

table_3pt <- data.frame("Name" = c("Steph Curry", "Draymond Green","Kevin Durant", "Andre Iguodala", "Klay Thompson"), "Total" = c(curry_3pt_total, draymond_3pt_total, durant_3pt_total, iguodala_3pt_total, klay_3pt_total), "Made" = c(curry_3pt_made, draymond_3pt_made, durant_3pt_made, iguodala_3pt_made, klay_3pt_made), "Perc_Made" = c(curry_3pt_percent, draymond_3pt_percent, durant_3pt_percent, iguodala_3pt_percent, klay_3pt_percent))
table_3pt$Perc_Made <- table_3pt$Perc_Made*100
table_3pt <- arrange(table_3pt, desc(table_3pt$Perc_Made))

```

```{r, message = F, warning = F, echo = F, results ='hide'}
#Effective Shooting & by Player
curry_total <- nrow(shot_data[shot_data$name == "Steph Curry",])
curry_made <- nrow(shot_data[shot_data$name == "Steph Curry" & shot_data$shot_made_flag == "shot_yes",])
curry_percent <- curry_made/curry_total

draymond_total <- nrow(shot_data[shot_data$name == "Draymond Green" ,])
draymond_made <- nrow(shot_data[shot_data$name == "Draymond Green"  & shot_data$shot_made_flag == "shot_yes",])
draymond_percent <- draymond_made/draymond_total

durant_total <- nrow(shot_data[shot_data$name == "Kevin Durant" ,])
durant_made <- nrow(shot_data[shot_data$name == "Kevin Durant"  & shot_data$shot_made_flag == "shot_yes",])
durant_percent <- durant_made/durant_total

iguodala_total <- nrow(shot_data[shot_data$name == "Andre Iguodala" ,])
iguodala_made <- nrow(shot_data[shot_data$name == "Andre Iguodala"  & shot_data$shot_made_flag == "shot_yes",])
iguodala_percent <- iguodala_made/iguodala_total

klay_total <- nrow(shot_data[shot_data$name == "Klay Thompson" ,])
klay_made <- nrow(shot_data[shot_data$name == "Klay Thompson"  & shot_data$shot_made_flag == "shot_yes",])
klay_percent <- klay_made/klay_total

table_overall <- data.frame("Name" = c("Steph Curry", "Draymond Green","Kevin Durant", "Andre Iguodala", "Klay Thompson"), "Total" = c(curry_total, draymond_total, durant_total, iguodala_total, klay_total), "Made" = c(curry_made, draymond_made, durant_made, iguodala_made, klay_made), "Perc_Made" = c(curry_percent, draymond_percent, durant_percent, iguodala_percent, klay_percent))
table_overall$Perc_Made <- table_overall$Perc_Made*100
table_overall <- arrange(table_overall, desc(table_overall$Perc_Made))

```

```{r, message = F, warning = F, echo = F, results ='hide'}
setwd("..")
curry <- read.csv("data/stephen-curry.csv", stringsAsFactors = FALSE)
klay <- read.csv("data/klay-thompson.csv", stringsAsFactors = FALSE)
durant <- read.csv("data/kevin-durant.csv", stringsAsFactors = FALSE)
draymond <- read.csv("data/draymond-green.csv", stringsAsFactors = FALSE)
iguodala <- read.csv("data/andre-iguodala.csv", stringsAsFactors = FALSE)

#adding name column
curry$name <- c("Steph Curry")
klay$name <- c("Klay Thompson")
durant$name <- c("Kevin Durant")
draymond$name <- c("Draymond Green")
iguodala$name <- c("Andre Iguodala")

#changing shot made values to be more descriptive
curry$shot_made_flag[curry$shot_made_flag == "n"] <- "shot_no"
curry$shot_made_flag[curry$shot_made_flag == "y"] <- "shot_yes"

klay$shot_made_flag[klay$shot_made_flag == "n"] <- "shot_no"
klay$shot_made_flag[klay$shot_made_flag == "y"] <- "shot_yes"

durant$shot_made_flag[durant$shot_made_flag == "n"] <- "shot_no"
durant$shot_made_flag[durant$shot_made_flag == "y"] <- "shot_yes"

draymond$shot_made_flag[draymond$shot_made_flag == "n"] <- "shot_no"
draymond$shot_made_flag[draymond$shot_made_flag == "y"] <- "shot_yes"

iguodala$shot_made_flag[iguodala$shot_made_flag == "n"] <- "shot_no"
iguodala$shot_made_flag[iguodala$shot_made_flag == "y"] <- "shot_yes"

#Adding column minutes
curry$minute <- (12*curry$period)-curry$minutes_remaining
klay$minute <- (12*klay$period)-klay$minutes_remaining
durant$minute <- (12*durant$period)-durant$minutes_remaining
draymond$minute <- (12*draymond$period)-draymond$minutes_remaining
iguodala$minute <- (12*iguodala$period)-iguodala$minutes_remaining

#Sinking files to output folder
sink("output/steph-curry-summary.txt")
summary(curry)
sink()

sink("output/klay-thompson-summary.txt")
summary(klay)
sink()

sink("output/kevin-durant-summary.txt")
summary(durant)
sink()

sink("output/draymond-green-summary.txt")
summary(draymond)
sink()

sink("output/andre-iguodala-summary.txt")
summary(iguodala)
sink()

#binding and exporting the tables
shot_data <- rbind(curry, klay, durant, draymond, iguodala)
write.csv(shot_data, file = "data/shots-data.csv")

#sinking the summary of the big table
sink("output/shot_data-summary.txt")
summary(shot_data)
sink()

```

```{r, message = F, warning = F, echo = F, results ='hide'}
setwd("..")
court_file <- "images/nba-court.jpg"

court_image <- rasterGrob(
  readJPEG(court_file),
  width = unit(1, "npc"),
  height = unit(1, "npc")
)

klay_scatterplot <- ggplot(data = klay) +
  annotation_custom(court_image, -250, 250, -50, 420) +
  geom_point(aes(x = x, y = y, color = shot_made_flag)) +
  ylim(-50,420) +
  ggtitle('Shot Chart: Klay Thompson (2016) ') +
  theme_minimal()

pdf(file = "images/klay-thompson-shot-chart.pdf", width = 6.5, height = 5)
klay_scatterplot
dev.off()


andre_scatterplot <- ggplot(data = iguodala) +
  annotation_custom(court_image, -250, 250, -50, 420) +
  geom_point(aes(x = x, y = y, color = shot_made_flag)) +
  ylim(-50,420) +
  ggtitle('Shot Chart: Andre Iguodala (2016) ') +
  theme_minimal()

pdf(file = "images/andre-iguodala-shot-chart.pdf", width = 6.5, height = 5)
andre_scatterplot
dev.off()


draymond_scatterplot <- ggplot(data = draymond) +
  annotation_custom(court_image, -250, 250, -50, 420) +
  geom_point(aes(x = x, y = y, color = shot_made_flag)) +
  ylim(-50,420) +
  ggtitle('Shot Chart: Draymond Green (2016) ') +
  theme_minimal()

pdf(file = "images/draymond-green-shot-chart.pdf", width = 6.5, height = 5)
draymond_scatterplot
dev.off()


kevin_scatterplot <- ggplot(data = durant) +
  annotation_custom(court_image, -250, 250, -50, 420) +
  geom_point(aes(x = x, y = y, color = shot_made_flag)) +
  ylim(-50,420) +
  ggtitle('Shot Chart: Kevin Durant (2016) ') +
  theme_minimal()

pdf(file = "images/kevin-durant-shot-chart.pdf", width = 6.5, height = 5)
kevin_scatterplot
dev.off()


steph_scatterplot <- ggplot(data = curry) +
  annotation_custom(court_image, -250, 250, -50, 420) +
  geom_point(aes(x = x, y = y, color = shot_made_flag)) +
  ylim(-50,420) +
  ggtitle('Shot Chart: Steph Curry (2016) ') +
  theme_minimal()

pdf(file = "images/steph-curry-shot-chart.pdf", width = 6.5, height = 5)
steph_scatterplot
dev.off()

# Faceting
shots_data <- read_csv("data/shots-data.csv")
all_players <- ggplot(data = shot_data) +
  annotation_custom(court_image, -250, 250, -50, 420) +
  geom_point(aes(x = x, y = y, color = shot_made_flag)) +
  ylim(-50,420) +
  ggtitle('Shot Chart: GSW (2016 season) ') +
  facet_wrap(~ name) +
  theme_minimal()

pdf(file = "images/gsw-shot-charts.pdf", width = 8, height = 7)
all_players
dev.off()

png(file = "images/gsw-shot-charts.png", width = 8, height = 7)
all_players
dev.off()

```
#Introduction  
Who is the best player on the Warriors? Is it KD or Steph? Is Draymond garbage? Is Iggy past his prime? Does Klay talk to his dog too much? In this article, we will take a look at the shooting percentages and shot selections of the Warriors to try to come to a conclusive ranking of the key players. Along the way, we will also take a look at the stylistic differences between key players.

#Motivation
While the Warriors are very good, they do not all play with the same style or even ability. Just by watching footage, it's clear that not everyone on the team is as good of a shooter as Steph or KD. Yet some more nuanced observations can be made about the types of shots being made between the players. For instance, Iggy and Draymond are clearly not as good as the other members of the team at scoring, but how do they compare to each other. At face value they both seem like similar players: offensive slashers with limted shooting capabilities. We will have to try and discern between them. And where does Klay fit into all of this? Can the stats help him make a suprise leapfrog over the two clear frontrunners in KD and Steph? Or does he have his own flaws that push him below the other two front court members?


#Data
Let's take a look at the shooting percentages, going by whether the shots taken were two pointers, three pointers, and then both combined.

First let's look at just the 2pt shots.

```{r, echo = FALSE}
table_2pt
```

Interestingly, Andre Iguodala has the highest percentage, but that's a bit miselading as he has the fewest shot attempts. Kevin Durant impresses here with not only the most shot attempts but also the second highest percentage.

Now looking at the 3 pointers.

```{r, echo = FALSE}
table_3pt
```

The splash brothers are the far and away the best shooters from here, top 2 in both volume and accuracy. Klay has the highest percentage, but Steph beats him in attempts by over 100. 

Combining both 2 point and 3 point attempts now:
```{r, echo = FALSE}
table_overall
```

Kevin Durant again takes the throne at the top of the charts, with a whopping 54% shooting percentage and being the third highest in attempts.Suprisingly, Steph is second to last here. It is also intersting to note that Draymond is at the bottom of the standings among all three scenarios.

And now let's look at the shot charts of the players. 

```{r, echo = FALSE, warning = FALSE}
all_players
```

While a bit hard to make definitive statements from these charts, the key takeaway is that only Durant, Klay, and Steph take a considerable amount of midrange shots. Additionally, Step Curry has a noticeable pull up on his shot chart, indicating that he takes shots from further back than the other players. 

#Analsysis

We will go over the five players in three chunks: Steph and Kd, Draymond and Iggy, and finally just Klay.

KD is better than Steph at shooting 2's as well as overall 2's and 3's, and has him beat in volume in both regards. On the other hand, Steph destroys Durant at shooting 3's where despite not being that much better percent wise, has almost triple Durant's volume. Which one wins here? Well even though Durant shoots better at 2's by 7% he only takes about 100 more than steph. Aditionally the aggregate of both 2's and 3's is a bit miselading here, since combining both shots doesn't makes the player who shoots 3's worse than the one who shoots 2's more, since the 3 pointer is a harder shot to hit since it's farther. The natural mean of these 2 shots should be different from each other, player to player. That leads to the main argument here: the 3 ball is just worth significantly more than the 2 ball. Curry shooting 3's generates 1.2 points per attempt more than anything KD can produce. Curry also takes his shots from farther back, as seen in the shot chart. This ability to strech and space the floor is Curry's most devstating ability, increasing the abilities of the other players on his team since he lures the defenders away from the basket. So while KD does have incredible production, he does not have the "magic" that Curry brings

Both Draymond and Iggy are not good to say the least, at shooting the ball. They are the 2 worst 3 point shooters of the starters. However, while Iggy at least shoots something reasonable, Draymond is atrocious at these shots, shooting 5% worse than Iggy. Even worse, he actually takes more shots than Andre as well. It's arguable that Draymond is a net negative on offense because of this. Defenders can sag off of him and guard other players, since they know Draymond is not a threat from outside. Even when Draymond goes in close, he's still the worst on the team at making 2 pointers! It's clear that Iggy beats out Draymond here. He doesn't shoot the ball very often, and when he does, you don't feel terrible about him shooting. Iggy plays his role, and doesn't bring the team down on their end of the floor. The same can't be said for Draymond.

Now on to Klay. Is there an argument for him being above KD? Sure he's a better three point shooter, the best on the team by percentage in fact. The difference between him and Steph, is the number of shots taken in this category, unfortunately for Klay. Klay simply doesn't shoot as much as Curry, so his high percentage doesn't mean as much. He also doesn't have Steph's gravity power, taking normal range 3's by comparison. And when it comes to the 2 point shots, he simply loses to KD. So while a very good player, he just doesn't have the firepower to move up the rankings. The good news for Klay though, is that he is clearly much better than Iggy. While Iggy tries to go even on offense, Klay actually does damage. He takes more shots, and makes them enough times for it to hurt, unlike Andre who takes very few shots by comparison, actually the least on the time.

#Conclusions

Based off the data and anlsyis we have seen, the rankings of the GSW players would have to be:

1. Steph Curry
2. Kevin Durant
3. Klay Thompson
4. Andre Iguodala
5. Draymond Green  

The inherit value of the 3 ball and Steph's overwhelming ability to make them put him at the top. Draymond loses out to Iggy by a considerable amount due to his horrendous efficiency and willingness to keep shooting in spite of his lack of ability. Klay while easily better than Andre, does not do enough to out power the sheer machine that is KD.










