---
title: "Workout 1"
author: "Justin Le"
output: github_document
---

```{r, message = F, warning = F, echo = FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(grid)
library(jpeg)
library(readr)
```

```{r, message = F, warning = F, echo = F, results ='hide'}
setwd("..")
shot_data <- read_csv("data/shots-data.csv")
```

```{r , message = F, warning = F, echo = F, results ='hide'}
#2pt effective shooting % by Player
curry_2pt_total <- nrow(shot_data[shot_data$name == "Steph Curry" & shot_data$shot_type == "2PT Field Goal",])
curry_2pt_made <- nrow(shot_data[shot_data$name == "Steph Curry" & shot_data$shot_type == "2PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
curry_2pt_percent <- curry_2pt_made/curry_2pt_total

draymond_2pt_total <- nrow(shot_data[shot_data$name == "Draymond Green" & shot_data$shot_type == "2PT Field Goal",])
draymond_2pt_made <- nrow(shot_data[shot_data$name == "Draymond Green" & shot_data$shot_type == "2PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
draymond_2pt_percent <- draymond_2pt_made/draymond_2pt_total

durant_2pt_total <- nrow(shot_data[shot_data$name == "Kevin Durant" & shot_data$shot_type == "2PT Field Goal",])
durant_2pt_made <- nrow(shot_data[shot_data$name == "Kevin Durant" & shot_data$shot_type == "2PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
durant_2pt_percent <- durant_2pt_made/durant_2pt_total

iguodala_2pt_total <- nrow(shot_data[shot_data$name == "Andre Iguodala" & shot_data$shot_type == "2PT Field Goal",])
iguodala_2pt_made <- nrow(shot_data[shot_data$name == "Andre Iguodala" & shot_data$shot_type == "2PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
iguodala_2pt_percent <- iguodala_2pt_made/iguodala_2pt_total

klay_2pt_total <- nrow(shot_data[shot_data$name == "Klay Thompson" & shot_data$shot_type == "2PT Field Goal",])
klay_2pt_made <- nrow(shot_data[shot_data$name == "Klay Thompson" & shot_data$shot_type == "2PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
klay_2pt_percent <- klay_2pt_made/klay_2pt_total

table_2pt <- data.frame("Name" = c("Steph Curry", "Draymond Green","Kevin Durant", "Andre Iguodala", "Klay Thompson"), "Total" = c(curry_2pt_total, draymond_2pt_total, durant_2pt_total, iguodala_2pt_total, klay_2pt_total), "Made" = c(curry_2pt_made, draymond_2pt_made, durant_2pt_made, iguodala_2pt_made, klay_2pt_made), "Perc_Made" = c(curry_2pt_percent, draymond_2pt_percent, durant_2pt_percent, iguodala_2pt_percent, klay_2pt_percent))
table_2pt$Perc_Made <- table_2pt$Perc_Made*100
table_2pt <- arrange(table_2pt, desc(table_2pt$Perc_Made))

```

```{r, message = F, warning = F, echo = F, results ='hide'}
#3pt effective shooting % by Player
curry_3pt_total <- nrow(shot_data[shot_data$name == "Steph Curry" & shot_data$shot_type == "3PT Field Goal",])
curry_3pt_made <- nrow(shot_data[shot_data$name == "Steph Curry" & shot_data$shot_type == "3PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
curry_3pt_percent <- curry_3pt_made/curry_3pt_total

draymond_3pt_total <- nrow(shot_data[shot_data$name == "Draymond Green" & shot_data$shot_type == "3PT Field Goal",])
draymond_3pt_made <- nrow(shot_data[shot_data$name == "Draymond Green" & shot_data$shot_type == "3PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
draymond_3pt_percent <- draymond_3pt_made/draymond_3pt_total

durant_3pt_total <- nrow(shot_data[shot_data$name == "Kevin Durant" & shot_data$shot_type == "3PT Field Goal",])
durant_3pt_made <- nrow(shot_data[shot_data$name == "Kevin Durant" & shot_data$shot_type == "3PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
durant_3pt_percent <- durant_3pt_made/durant_3pt_total

iguodala_3pt_total <- nrow(shot_data[shot_data$name == "Andre Iguodala" & shot_data$shot_type == "3PT Field Goal",])
iguodala_3pt_made <- nrow(shot_data[shot_data$name == "Andre Iguodala" & shot_data$shot_type == "3PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
iguodala_3pt_percent <- iguodala_3pt_made/iguodala_3pt_total

klay_3pt_total <- nrow(shot_data[shot_data$name == "Klay Thompson" & shot_data$shot_type == "3PT Field Goal",])
klay_3pt_made <- nrow(shot_data[shot_data$name == "Klay Thompson" & shot_data$shot_type == "3PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
klay_3pt_percent <- klay_3pt_made/klay_3pt_total

table_3pt <- data.frame("Name" = c("Steph Curry", "Draymond Green","Kevin Durant", "Andre Iguodala", "Klay Thompson"), "Total" = c(curry_3pt_total, draymond_3pt_total, durant_3pt_total, iguodala_3pt_total, klay_3pt_total), "Made" = c(curry_3pt_made, draymond_3pt_made, durant_3pt_made, iguodala_3pt_made, klay_3pt_made), "Perc_Made" = c(curry_3pt_percent, draymond_3pt_percent, durant_3pt_percent, iguodala_3pt_percent, klay_3pt_percent))
table_3pt$Perc_Made <- table_3pt$Perc_Made*100
table_3pt <- arrange(table_3pt, desc(table_3pt$Perc_Made))

```

```{r, message = F, warning = F, echo = F, results ='hide'}
#Effective Shooting & by Player
curry_total <- nrow(shot_data[shot_data$name == "Steph Curry",])
curry_made <- nrow(shot_data[shot_data$name == "Steph Curry" & shot_data$shot_made_flag == "shot_yes",])
curry_percent <- curry_made/curry_total

draymond_total <- nrow(shot_data[shot_data$name == "Draymond Green" ,])
draymond_made <- nrow(shot_data[shot_data$name == "Draymond Green"  & shot_data$shot_made_flag == "shot_yes",])
draymond_percent <- draymond_made/draymond_total

durant_total <- nrow(shot_data[shot_data$name == "Kevin Durant" ,])
durant_made <- nrow(shot_data[shot_data$name == "Kevin Durant"  & shot_data$shot_made_flag == "shot_yes",])
durant_percent <- durant_made/durant_total

iguodala_total <- nrow(shot_data[shot_data$name == "Andre Iguodala" ,])
iguodala_made <- nrow(shot_data[shot_data$name == "Andre Iguodala"  & shot_data$shot_made_flag == "shot_yes",])
iguodala_percent <- iguodala_made/iguodala_total

klay_total <- nrow(shot_data[shot_data$name == "Klay Thompson" ,])
klay_made <- nrow(shot_data[shot_data$name == "Klay Thompson"  & shot_data$shot_made_flag == "shot_yes",])
klay_percent <- klay_made/klay_total

table_overall <- data.frame("Name" = c("Steph Curry", "Draymond Green","Kevin Durant", "Andre Iguodala", "Klay Thompson"), "Total" = c(curry_total, draymond_total, durant_total, iguodala_total, klay_total), "Made" = c(curry_made, draymond_made, durant_made, iguodala_made, klay_made), "Perc_Made" = c(curry_percent, draymond_percent, durant_percent, iguodala_percent, klay_percent))
table_overall$Perc_Made <- table_overall$Perc_Made*100
table_overall <- arrange(table_overall, desc(table_overall$Perc_Made))

```

```{r, message = F, warning = F, echo = F, results ='hide'}
setwd("..")
curry <- read.csv("data/stephen-curry.csv", stringsAsFactors = FALSE)
klay <- read.csv("data/klay-thompson.csv", stringsAsFactors = FALSE)
durant <- read.csv("data/kevin-durant.csv", stringsAsFactors = FALSE)
draymond <- read.csv("data/draymond-green.csv", stringsAsFactors = FALSE)
iguodala <- read.csv("data/andre-iguodala.csv", stringsAsFactors = FALSE)

#adding name column
curry$name <- c("Steph Curry")
klay$name <- c("Klay Thompson")
durant$name <- c("Kevin Durant")
draymond$name <- c("Draymond Green")
iguodala$name <- c("Andre Iguodala")

#changing shot made values to be more descriptive
curry$shot_made_flag[curry$shot_made_flag == "n"] <- "shot_no"
curry$shot_made_flag[curry$shot_made_flag == "y"] <- "shot_yes"

klay$shot_made_flag[klay$shot_made_flag == "n"] <- "shot_no"
klay$shot_made_flag[klay$shot_made_flag == "y"] <- "shot_yes"

durant$shot_made_flag[durant$shot_made_flag == "n"] <- "shot_no"
durant$shot_made_flag[durant$shot_made_flag == "y"] <- "shot_yes"

draymond$shot_made_flag[draymond$shot_made_flag == "n"] <- "shot_no"
draymond$shot_made_flag[draymond$shot_made_flag == "y"] <- "shot_yes"

iguodala$shot_made_flag[iguodala$shot_made_flag == "n"] <- "shot_no"
iguodala$shot_made_flag[iguodala$shot_made_flag == "y"] <- "shot_yes"

#Adding column minutes
curry$minute <- (12*curry$period)-curry$minutes_remaining
klay$minute <- (12*klay$period)-klay$minutes_remaining
durant$minute <- (12*durant$period)-durant$minutes_remaining
draymond$minute <- (12*draymond$period)-draymond$minutes_remaining
iguodala$minute <- (12*iguodala$period)-iguodala$minutes_remaining

#Sinking files to output folder
sink("output/steph-curry-summary.txt")
summary(curry)
sink()

sink("output/klay-thompson-summary.txt")
summary(klay)
sink()

sink("output/kevin-durant-summary.txt")
summary(durant)
sink()

sink("output/draymond-green-summary.txt")
summary(draymond)
sink()

sink("output/andre-iguodala-summary.txt")
summary(iguodala)
sink()

#binding and exporting the tables
shot_data <- rbind(curry, klay, durant, draymond, iguodala)
write.csv(shot_data, file = "data/shots-data.csv")

#sinking the summary of the big table
sink("output/shot_data-summary.txt")
summary(shot_data)
sink()

```

```{r, message = F, warning = F, echo = F, results ='hide'}
setwd("..")
court_file <- "images/nba-court.jpg"

court_image <- rasterGrob(
  readJPEG(court_file),
  width = unit(1, "npc"),
  height = unit(1, "npc")
)

klay_scatterplot <- ggplot(data = klay) +
  annotation_custom(court_image, -250, 250, -50, 420) +
  geom_point(aes(x = x, y = y, color = shot_made_flag)) +
  ylim(-50,420) +
  ggtitle('Shot Chart: Klay Thompson (2016) ') +
  theme_minimal()

pdf(file = "images/klay-thompson-shot-chart.pdf", width = 6.5, height = 5)
klay_scatterplot
dev.off()


andre_scatterplot <- ggplot(data = iguodala) +
  annotation_custom(court_image, -250, 250, -50, 420) +
  geom_point(aes(x = x, y = y, color = shot_made_flag)) +
  ylim(-50,420) +
  ggtitle('Shot Chart: Andre Iguodala (2016) ') +
  theme_minimal()

pdf(file = "images/andre-iguodala-shot-chart.pdf", width = 6.5, height = 5)
andre_scatterplot
dev.off()


draymond_scatterplot <- ggplot(data = draymond) +
  annotation_custom(court_image, -250, 250, -50, 420) +
  geom_point(aes(x = x, y = y, color = shot_made_flag)) +
  ylim(-50,420) +
  ggtitle('Shot Chart: Draymond Green (2016) ') +
  theme_minimal()

pdf(file = "images/draymond-green-shot-chart.pdf", width = 6.5, height = 5)
draymond_scatterplot
dev.off()


kevin_scatterplot <- ggplot(data = durant) +
  annotation_custom(court_image, -250, 250, -50, 420) +
  geom_point(aes(x = x, y = y, color = shot_made_flag)) +
  ylim(-50,420) +
  ggtitle('Shot Chart: Kevin Durant (2016) ') +
  theme_minimal()

pdf(file = "images/kevin-durant-shot-chart.pdf", width = 6.5, height = 5)
kevin_scatterplot
dev.off()


steph_scatterplot <- ggplot(data = curry) +
  annotation_custom(court_image, -250, 250, -50, 420) +
  geom_point(aes(x = x, y = y, color = shot_made_flag)) +
  ylim(-50,420) +
  ggtitle('Shot Chart: Steph Curry (2016) ') +
  theme_minimal()

pdf(file = "images/steph-curry-shot-chart.pdf", width = 6.5, height = 5)
steph_scatterplot
dev.off()

# Faceting
shots_data <- read_csv("data/shots-data.csv")
all_players <- ggplot(data = shot_data) +
  annotation_custom(court_image, -250, 250, -50, 420) +
  geom_point(aes(x = x, y = y, color = shot_made_flag)) +
  ylim(-50,420) +
  ggtitle('Shot Chart: GSW (2016 season) ') +
  facet_wrap(~ name) +
  theme_minimal()

pdf(file = "images/gsw-shot-charts.pdf", width = 8, height = 7)
all_players
dev.off()

png(file = "images/gsw-shot-charts.png", width = 8, height = 7)
all_players
dev.off()

```
#Introduction  
Who is the best player on the Warriors? Is it KD or Steph? Is Draymond garbage? Is Iggy past his prime? In this article, we will take a look at the shooting percentages and shot selections of the Warriors to try to come to a conclusive ranking of the key players. Along the way, we will also take a look at the stylistic differences between key players.

#Motivation
While the Warriors are very good, they do not all play with the same style or even ability. Just by watching footage, it's clear that not everyone on the team is as good of a shooter as Steph or KD. Yet some more nuanced observations can be mad


#Data
Let's take a look at the shooting percentages, going by whether the shots taken were two pointers, three pointers, and then both combined.

First let's look at just the 2pt shots.

```{r, echo = FALSE}
table_2pt
```

Interestingly, Andre Iguodala has the highest percentage, but that's a bit miselading as he has the fewest shot attempts. Kevin Durant impresses here with not only the most shot attempts but also the second highest percentage.

Now looking at the 3 pointers.

```{r, echo = FALSE}
table_3pt
```

The splash brothers are the far and away the best shooters from here, top 2 in both volume and accuracy. Klay has the highest percentage, but Steph beats him in attempts by over 100. 

Combining both 2 point and 3 point attempts now:
```{r, echo = FALSE}
table_overall
```

Kevin Durant again takes the throne at the top of the charts, with a whopping 54% shooting percentage and being the third highest in attempts.Suprisingly, Steph is second to last here. It is also intersting to note that Draymond is at the bottom of the standings among all three scenarios.

And now let's look at the shot charts of the players. 

```{r, echo = FALSE, warning = FALSE}
all_players
```

While a bit hard to make definitive statements from these charts, the key takeaway is that only Durant, Klay, and Steph take a considerable amount of midrange shots. Additionally, Step Curry has a noticeable pull up on his shot chart, indicating that he takes shots from further back than the other players. 

#Analsysis

Steph's overwhelming advantage at shooting the 3 ball edges him over Durant.Draymond loses out to Iguodala because of his horrendous shooting at considerable volume. Iguodala at least understands he is playing with better players and thus limits his shots. Despite being suprisingly efficient at times, his lack of volume puts him below Klay.

#Conclusions

Based off the data and anlsyis we have seen, the rankings of the GSW players would have to be:

1. Steph Curry
2. Kevin Durant
3. Klay Thompson
4. Andre Iguodala
5. Draymond Green











