---
title: "Workout 1"
author: "Justin Le"
output: github_document
---

```{r, message = F, warning = F}
library(readr)
library(dplyr)

```

```{r, message = F, warning = F, echo = F}
setwd("..")
shot_data <- read_csv("data/shots-data.csv")
```

```{r , message = F, warning = F, echo = F}
#2pt effective shooting % by Player
curry_2pt_total <- nrow(shot_data[shot_data$name == "Steph Curry" & shot_data$shot_type == "2PT Field Goal",])
curry_2pt_made <- nrow(shot_data[shot_data$name == "Steph Curry" & shot_data$shot_type == "2PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
curry_2pt_percent <- curry_2pt_made/curry_2pt_total

draymond_2pt_total <- nrow(shot_data[shot_data$name == "Draymond Green" & shot_data$shot_type == "2PT Field Goal",])
draymond_2pt_made <- nrow(shot_data[shot_data$name == "Draymond Green" & shot_data$shot_type == "2PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
draymond_2pt_percent <- draymond_2pt_made/draymond_2pt_total

durant_2pt_total <- nrow(shot_data[shot_data$name == "Kevin Durant" & shot_data$shot_type == "2PT Field Goal",])
durant_2pt_made <- nrow(shot_data[shot_data$name == "Kevin Durant" & shot_data$shot_type == "2PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
durant_2pt_percent <- durant_2pt_made/durant_2pt_total

iguodala_2pt_total <- nrow(shot_data[shot_data$name == "Andre Iguodala" & shot_data$shot_type == "2PT Field Goal",])
iguodala_2pt_made <- nrow(shot_data[shot_data$name == "Andre Iguodala" & shot_data$shot_type == "2PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
iguodala_2pt_percent <- iguodala_2pt_made/iguodala_2pt_total

klay_2pt_total <- nrow(shot_data[shot_data$name == "Klay Thompson" & shot_data$shot_type == "2PT Field Goal",])
klay_2pt_made <- nrow(shot_data[shot_data$name == "Klay Thompson" & shot_data$shot_type == "2PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
klay_2pt_percent <- klay_2pt_made/klay_2pt_total

table_2pt <- data.frame("Name" = c("Steph Curry", "Draymond Green","Kevin Durant", "Andre Iguodala", "Klay Thompson"), "Total" = c(curry_2pt_total, draymond_2pt_total, durant_2pt_total, iguodala_2pt_total, klay_2pt_total), "Made" = c(curry_2pt_made, draymond_2pt_made, durant_2pt_made, iguodala_2pt_made, klay_2pt_made), "Perc_Made" = c(curry_2pt_percent, draymond_2pt_percent, durant_2pt_percent, iguodala_2pt_percent, klay_2pt_percent))
table_2pt$Perc_Made <- table_2pt$Perc_Made*100
table_2pt <- arrange(table_2pt, desc(table_2pt$Perc_Made))

```

```{r, message = F, warning = F, echo = F}
#3pt effective shooting % by Player
curry_3pt_total <- nrow(shot_data[shot_data$name == "Steph Curry" & shot_data$shot_type == "3PT Field Goal",])
curry_3pt_made <- nrow(shot_data[shot_data$name == "Steph Curry" & shot_data$shot_type == "3PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
curry_3pt_percent <- curry_3pt_made/curry_3pt_total

draymond_3pt_total <- nrow(shot_data[shot_data$name == "Draymond Green" & shot_data$shot_type == "3PT Field Goal",])
draymond_3pt_made <- nrow(shot_data[shot_data$name == "Draymond Green" & shot_data$shot_type == "3PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
draymond_3pt_percent <- draymond_3pt_made/draymond_3pt_total

durant_3pt_total <- nrow(shot_data[shot_data$name == "Kevin Durant" & shot_data$shot_type == "3PT Field Goal",])
durant_3pt_made <- nrow(shot_data[shot_data$name == "Kevin Durant" & shot_data$shot_type == "3PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
durant_3pt_percent <- durant_3pt_made/durant_3pt_total

iguodala_3pt_total <- nrow(shot_data[shot_data$name == "Andre Iguodala" & shot_data$shot_type == "3PT Field Goal",])
iguodala_3pt_made <- nrow(shot_data[shot_data$name == "Andre Iguodala" & shot_data$shot_type == "3PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
iguodala_3pt_percent <- iguodala_3pt_made/iguodala_3pt_total

klay_3pt_total <- nrow(shot_data[shot_data$name == "Klay Thompson" & shot_data$shot_type == "3PT Field Goal",])
klay_3pt_made <- nrow(shot_data[shot_data$name == "Klay Thompson" & shot_data$shot_type == "3PT Field Goal" & shot_data$shot_made_flag == "shot_yes",])
klay_3pt_percent <- klay_3pt_made/klay_3pt_total

table_3pt <- data.frame("Name" = c("Steph Curry", "Draymond Green","Kevin Durant", "Andre Iguodala", "Klay Thompson"), "Total" = c(curry_3pt_total, draymond_3pt_total, durant_3pt_total, iguodala_3pt_total, klay_3pt_total), "Made" = c(curry_3pt_made, draymond_3pt_made, durant_3pt_made, iguodala_3pt_made, klay_3pt_made), "Perc_Made" = c(curry_3pt_percent, draymond_3pt_percent, durant_3pt_percent, iguodala_3pt_percent, klay_3pt_percent))
table_3pt$Perc_Made <- table_3pt$Perc_Made*100
table_3pt <- arrange(table_3pt, desc(table_3pt$Perc_Made))

```

```{r, message = F, warning = F, echo = F}
#Effective Shooting & by Player
curry_total <- nrow(shot_data[shot_data$name == "Steph Curry",])
curry_made <- nrow(shot_data[shot_data$name == "Steph Curry" & shot_data$shot_made_flag == "shot_yes",])
curry_percent <- curry_made/curry_total

draymond_total <- nrow(shot_data[shot_data$name == "Draymond Green" ,])
draymond_made <- nrow(shot_data[shot_data$name == "Draymond Green"  & shot_data$shot_made_flag == "shot_yes",])
draymond_percent <- draymond_made/draymond_total

durant_total <- nrow(shot_data[shot_data$name == "Kevin Durant" ,])
durant_made <- nrow(shot_data[shot_data$name == "Kevin Durant"  & shot_data$shot_made_flag == "shot_yes",])
durant_percent <- durant_made/durant_total

iguodala_total <- nrow(shot_data[shot_data$name == "Andre Iguodala" ,])
iguodala_made <- nrow(shot_data[shot_data$name == "Andre Iguodala"  & shot_data$shot_made_flag == "shot_yes",])
iguodala_percent <- iguodala_made/iguodala_total

klay_total <- nrow(shot_data[shot_data$name == "Klay Thompson" ,])
klay_made <- nrow(shot_data[shot_data$name == "Klay Thompson"  & shot_data$shot_made_flag == "shot_yes",])
klay_percent <- klay_made/klay_total

table_overall <- data.frame("Name" = c("Steph Curry", "Draymond Green","Kevin Durant", "Andre Iguodala", "Klay Thompson"), "Total" = c(curry_total, draymond_total, durant_total, iguodala_total, klay_total), "Made" = c(curry_made, draymond_made, durant_made, iguodala_made, klay_made), "Perc_Made" = c(curry_percent, draymond_percent, durant_percent, iguodala_percent, klay_percent))
table_overall$Perc_Made <- table_overall$Perc_Made*100
table_overall <- arrange(table_overall, desc(table_overall$Perc_Made))


```

#Introduction  
With the amassing of numerous stars on the Golden State Roster, the natural question to ask is who is the best offensive player? In this article, we will look at the shoot percentages of the main players on Golden State, and try to sort them by offensive ability. It will be important to tak into consideration the Warrior's historic reliance and skill of shooting the three ball, with the inclusion of Kevin Durant's lethality from the midrange. 







